---
title: "Understanding Trade"
author:
- familyname: Jaiswal
  othernames: Prachi
  address: Monash University
  email: "pjai0005@student.monash.edu"
  correspondingauthor: true
  qualifications:  Undergraduate
- familyname: Jiang
  othernames: Yuwei
  address: Monash Universtidy
  email: "yjia0142@student.monash.edu"
  correspondingauthor: true
  qualifications: Master
- familyname: Jawahar
  othernames: Sithalakshmi 
  address: Monash University
  email: "sjaw002@student.monash.edu"
  correspondingauthor: true
  qualifications:  Undergraduate  
department: Monash University \newline Business and Economics
organization: ETC5513 Assignment4 Team Nemo
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---
```{r , include=FALSE}

 knitr::opts_chunk$set(fig.pos = "H", out.extra = "",  echo = FALSE, message = FALSE, warning = FALSE)

# Libraries
library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(maps)
```

```{r}
clean <- function(x, y) {
  read.csv(x) %>% 
  select(Country.or.Area: Trade..USD.) %>% 
  rename( Country = "Country.or.Area", Trade ="Trade..USD." ) %>% 
  mutate(Category = factor(y)) %>% 
  select(-Commodity)
}


iron_steel <- clean("data/UNdata_Export_20210520_091706592.csv", "iron_steel")
fruits_nuts <- clean("data/UNdata_Export_20210520_092512505.csv", "fruits_nuts")
rubber <- clean("data/UNdata_Export_20210520_092039303.csv", "rubber")
cars <- clean("data/UNdata_Export_20210519_132226922.csv","cars")
coffee <- clean("data/UNdata_Export_20210519_133347537.csv","coffee")
cotton <- clean("data/UNdata_Export_20210519_132629219.csv","cotton")
pharma <- clean("data/UNdata_Export_20210519_132341600.csv","pharma")
sugar <- clean("data/UNdata_Export_20210519_132821334.csv","sugar")
tobacco <- clean("data/UNdata_Export_20210519_131835858.csv","tobacco")
wheat <- clean("data/UNdata_Export_20210519_132931178.csv","wheat")

```

```{r}
team_nemo<- rbind(iron_steel, fruits_nuts, rubber, cars, coffee, cotton, pharma, sugar, tobacco, wheat)
assign4 <- write_csv(team_nemo, "data/team_nemo.csv")
```



\section*{Introduction}

```{r}
final <- read.csv("data/team_nemo.csv")
```



\section*{Germany}

\section*{China}
# The trades of China

It is reported from Wikipedia(2020) that China has become the world's largest economy by GDP. Due to the rapid growth of China's economy, Chinese trade has expanded at a breakneck pace. This section will concentrate on the analysis of China's performance on world's major varieties of trade.

## Import Trades of China from 2016 to 2018

```{r include=FALSE}
China_ip <- final %>% filter(Country=="China") %>%
  filter(Flow=="Import")
China_ep <- final %>% filter(Country=="China") %>%
  filter(Flow=="Export")
```

```{r include=FALSE}
China1 <- China_ip %>% group_by(Category, Year) %>%
  summarise(n=sum(Trade)) %>%
  mutate(Trade=n/1000000000) %>%
  mutate(Year=as.factor(Year))

China_import1 <- ggplot(China1 ,
               mapping=aes(x=reorder(Category, Trade),y=Trade))+
  geom_bar(stat="identity", position="dodge", aes(fill=Year), width = 0.6)+
  scale_fill_brewer(palette = 'Accent')+
  scale_y_continuous(labels=scales::dollar_format())+
  xlab("Category") +
    ylab("Trade(b)") +
  theme(legend.position="bottom", legend.key.size = unit(0.1, "inches"), axis.text.x = element_text(angle=30,
                                   hjust=1,
                                   size=8))
China_import1
```


```{r include=FALSE}
China_import2 <- ggplot(China1, aes(x = Year,
    y = Trade, 
    color= Category, group = Category)) +
    geom_line() +
  scale_y_continuous(labels=scales::dollar_format())+
    xlab("Year") +
    ylab("Trade(b)") +
  theme(legend.position="bottom", legend.key.size = unit(0.02, "inches"))+
  geom_point()
    
China_import2 
```


```{r Yuweiplot1, fig.cap= "Important Import Trade of China From 2016 to 2018", fig.show="hold", out.width="100%", out.width="100%",echo=FALSE, warning=FALSE, message=FALSE}
Import <- ggarrange(China_import1, China_import2,  
           ncol =2)
annotate_figure(Import,
                top = text_grob("Important Import Trades of China from 2016 to 2018", face = "bold", size = 12))
```
From the Figure \@ref(fig:Yuweiplot1), it could be concluded that cars, pharma,  iron_steel and rubber are the top four categories that China imported from 2016 to 2018. At the same time, coffee, wheat, sugar and tobacco are not so prosperous among China's import trades. It is worth noting that the total volumes of cars' trades in each year are much higher than that of the second place. When look at the right part of the Figure \@ref(fig:Yuweiplot1), the trade tendencies of the most categories are going smoothly or upward, except for rubber.


\section*{United States of America}

\section*{Conclusion}



