---
title: "Understanding Trade"
author:
- familyname: Jaiswal
  othernames: Prachi
  address: Monash University
  email: "pjai0005@student.monash.edu"
  correspondingauthor: true
  qualifications:  Undergraduate
- familyname: Jiang
  othernames: Yuwei
  address: Monash Universtidy
  email: "yjia0142@student.monash.edu"
  correspondingauthor: true
  qualifications: Master
- familyname: Jawahar
  othernames: Sithalakshmi 
  address: Monash University
  email: "sjaw002@student.monash.edu"
  correspondingauthor: true
  qualifications:  Undergraduate  
department: Monash University \newline Business and Economics
organization: ETC5513 Assignment4 Team Nemo
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---
```{r , include=FALSE}

 knitr::opts_chunk$set(fig.pos = "H", out.extra = "",  echo = FALSE, message = FALSE, warning = FALSE)

# Libraries
library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(maps)
```

```{r}
clean <- function(x, y) {
  read.csv(x) %>% 
  select(Country.or.Area: Trade..USD.) %>% 
  rename( Country = "Country.or.Area", Trade ="Trade..USD." ) %>% 
  mutate(Category = factor(y)) %>% 
  select(-Commodity)
}


iron_steel <- clean("data/UNdata_Export_20210520_091706592.csv", "iron_steel")
fruits_nuts <- clean("data/UNdata_Export_20210520_092512505.csv", "fruits_nuts")
rubber <- clean("data/UNdata_Export_20210520_092039303.csv", "rubber")
cars <- clean("data/UNdata_Export_20210519_132226922.csv","cars")
coffee <- clean("data/UNdata_Export_20210519_133347537.csv","coffee")
cotton <- clean("data/UNdata_Export_20210519_132629219.csv","cotton")
pharma <- clean("data/UNdata_Export_20210519_132341600.csv","pharma")
sugar <- clean("data/UNdata_Export_20210519_132821334.csv","sugar")
tobacco <- clean("data/UNdata_Export_20210519_131835858.csv","tobacco")
wheat <- clean("data/UNdata_Export_20210519_132931178.csv","wheat")

```

```{r}
team_nemo<- rbind(iron_steel, fruits_nuts, rubber, cars, coffee, cotton, pharma, sugar, tobacco, wheat)
assign4 <- write_csv(team_nemo, "data/team_nemo.csv")
```



\section*{Introduction}

```{r}
final <- read.csv("data/team_nemo.csv")
```



\section*{Germany}

\section*{China}

\section*{United States of America}

## Understanding the trend

```{r plot1, fig.cap= "Flow of goods", out.width="100%", fig.show="hold" }
usa <- final %>% 
filter(Country == "USA") %>% 
  mutate(Trade = Trade/1000000000) %>% 
    filter(Flow != "Re-Export")
  
ggplot(usa, 
       mapping=aes(x=reorder(Category, Trade),y=Trade)) +
  aes(fill=Flow)+
 geom_col(position = "dodge") +
  facet_grid(~ Year)+
  scale_y_continuous(labels = scales::dollar) +
  scale_fill_manual(values=c("#c384e8", "#5fc2ac" ))+ 
  xlab("Trade Category") + 
  ggtitle("Comparing Inflow and Outflow through the years")+
  theme(axis.text.x = element_text(angle=90,
                                   hjust=1,
                                   size=8)) 
  
```

 From \@ref(fig:plot1) It is obvious that cars are the most traded goods. Even though USA has its own In-house production unit for car brands like Jeep, Ford and Chevrolet it still seems to import a lot of cars at a value of almost 100 billion. Followed by Pharmaceutical products and rubber contributing highly. 
 
Even though USA imports more than it exports, goods like Cotton, fruits and nuts, iron and steel the exports are higher than imports. 




\section*{Conclusion}



